Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 payment-proof.tex
fixes to thm 2
finished edits of proof of Theorem 2

\begin{rtheorem}{Theorem}{\ref{rst:budget}}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right).  \nonumber 
\end{align}
\end{rtheorem}

@@

Next, we show that for any sample path \SP in the envelope \Env{\ell},
we can bound the total number of payments made in terms of $\ell$.
Define $h(\ell) := \max \left( \exp(\frac{2}{\MinProb}),
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)$.

@@

\begin{proof}
The proof is similar to that of Lemma~\ref{lem:numP}.
Fix a sample path $\SP \in \Env{\ell}$.
Consider a phase $s > h(\ell)$ and a time $t$ in phase $s$.
Because $\SP \in \Env{\ell}$, in particular, all estimation errors are
bounded at time $t$, in the sense that the event \AccEU{t}{g(s,\ell)}
happens.
Because $s \geq h(\ell)$, we get that
$g(s,\ell) \leq \frac{\MinProb}{4 \Diam d \TieDensity}$
as well as $s \geq \exp(2/\MinProb)$.
Therefore, we can apply Lemma~\ref{lem:no-incentives} and conclude
that the pull at time $t$ was not incentivized.
\end{proof}

@@

\begin{align*}
O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right)
& = 
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma
\cdot \exp(\frac{2}{\MinProb}) \right).
\end{align*}
\end{extraproof}

>>>>

\begin{rtheorem}{Theorem}{\ref{rst:budget}}
The expected total payment of
Algorithm~\ref{alg:basic-incentivizing} is at most
$O \left(\ARMNUM^2 \cdot \e^{2/\MinProb} \right)$.
%The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
%\begin{align}
% O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp\left(\frac{2}{\MinProb}\right) \right).  
%\pfedit{O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot \max\bigg\{\exp\left(\frac{2}{p}\right),
%\left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
%\left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}
%\right).}\nonumber 
%\end{align}
\pfcomment{Maybe we want to simplify the constants in the above? Not sure.}
\dkcomment{I think that stating it the way we state it in Section 3
  makes the most sense.}
\end{rtheorem}

@@

Next, we show that for any sample path \SP in the envelope \Env{\ell},
we can bound the total number of payments made in terms of $\ell$.
Define $h(\ell) := \max \left( \exp(\frac{2}{\MinProb}),
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)$.

@@

\begin{proof}
The proof is similar to that of Lemma~\ref{lem:numP}.
Fix a sample path $\SP \in \Env{\ell}$.
Consider a phase $s > h(\ell)$ and a time $t$ in phase $s$.
Because $\SP \in \Env{\ell}$, in particular, all estimation errors are
bounded at time $t$, in the sense that the event \AccEU{t}{g(s,\ell)}
happens.
Because $s \geq h(\ell)$, we get that
$g(s,\ell) \leq \min(\frac{\TieCutoff}{2\Diam d}, \frac{\MinProb}{4 \Diam d \TieDensity})$
as well as $s \geq \exp(2/\MinProb)$.
Therefore, we can apply Lemma~\ref{lem:no-incentives} and conclude
that the pull at time $t$ was not incentivized.
\end{proof}

@@

\begin{align*}
& O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1)
  \right)
\\ = 
& O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
  \max \left( \exp \left(\frac{2}{\MinProb}\right),
		    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
    \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2} \right)
\right)
\\ =
& \dkedit{O \left( \ARMNUM^2 \cdot \exp \left(\frac{2}{\MinProb} \right) \right)}.
\end{align*}
\end{extraproof}
